---
title: "Direct inhibition of the NOTCH transcription factor complex"
author: "Document Author"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

## Introducción
## Objetivos
##  Métodos
## Resultados
## Discusión

`html_pretty` in the [**prettydoc**](http://github.com/yixuan/prettydoc/)
package is a new output format for creating HTML document from R Markdown files.
`html_pretty` is more lightweight compared to `html_document`, and is more
stylish than `html_vignette` when creating package vignettes.

## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and
`architect`), and two syntax highlight styles (`github` and `vignette`).
The theme and highlight styles can be specified in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

```{r fig.width=6, fig.height=6, fig.align='center'}
###### 1. Instalación de paquetes necesarios para la realización de este ejercicio#####

# Geo Query
# http://www.bioconductor.org/packages/release/bioc/html/GEOquery.html
# Paquete que permite descargar del repositorio GEO (Gene Expression Omnibus) conjuntos de microarrays
if (!("GEOquery" %in% installed.packages())) { 
  source("http://www.bioconductor.org/biocLite.R"); 
  biocLite("GEOquery");
}


# AFFY
# http://www.bioconductor.org/packages/3.2/bioc/html/affy.html
# Paquete que contiene funciones para el análisis de datos de microarrays de oligonucleótidos (Affymetrix)
if (!("affy" %in% installed.packages())) { 
  source("http://www.bioconductor.org/biocLite.R"); 
  biocLite("affy");
}


## AFFYPLM
# http://www.bioconductor.org/packages/release/bioc/html/affyPLM.html
# Paquete que extiende y mejora la funcionalidad del paquete affy (herramientas de análisis de calidad)
if (!("affyPLM" %in% installed.packages())) { 
  source("http://www.bioconductor.org/biocLite.R"); 
  biocLite("affyPLM");
}


## GENEFILTER
# http://www.bioconductor.org/packages/release/bioc/html/genefilter.html
# Paquete que proporciona funciones para el filtrado de genes a partir de un conjunto de microarrays
if (!("genefilter" %in% installed.packages())) { 
  source("http://www.bioconductor.org/biocLite.R"); 
  biocLite("genefilter");
}


# LIMMA
# http://www.bioconductor.org/packages/3.2/bioc/html/limma.html
# Paquete para el análisis de expresión diferencial en microarrays, aunque contiene mucha funcionalidad adicional para el análisis de microarrays
if (!("limma" %in% installed.packages())) { 
  source("http://www.bioconductor.org/biocLite.R"); 
  biocLite("limma");
}


# hgu133plus2
# http://www.bioconductor.org/packages/3.2/data/annotation/html/hgu133plus2.db.html
# Paquete de anotación -> nos indica la correspondencia entre las sondas y el gen al que representa, entre otro tipo de información de anotación: términos GO, Entrez IDs, cromosoma, etc
if (!("hgu133plus2.db" %in% installed.packages())) { 
  source("http://www.bioconductor.org/biocLite.R"); 
  biocLite("hgu133plus2.db");
}

# KEGGREST
# http://www.bioconductor.org/packages/release/bioc/html/KEGGREST.html
# Paquete que proporciona una interfaz con el servidor KEGG REST
if (!("KEGGREST" %in% installed.packages())) { 
  source("http://www.bioconductor.org/biocLite.R"); 
  biocLite("KEGGREST");
}

install.packages("ggfortify")
library(ggfortify)
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
library(hgu133plus2.db)
library(GEOquery)
library(affy)
library(affyPLM)
library(genefilter)
library(limma)
library(hgu133plus2.db)
library(KEGGREST)
library(ggbiplot)
```

You can include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](http://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.
